The Lipid Interactome Repository

### 2025-03-31 BioinformaticsApplicationNote/GG_2025_applicationNote.qmd
Adding Yu et al 2021 to yaml, adding JMB edits to manuscript

copyright:
  holder: "Gaelen Guzman"
  year: 2025
authors:
  - name: "Gaelen Guzman"
    affiliations:
      - name:  "Oregon Health & Science University"
        address: 3222 SW Research Dr
        city: Portland
        state: OR
        postal-code: 97239
    orcid: 0000-0002-7696-6034
    corresponding: true
    email: gaelen.guzman@lipidinteractome.org
  - name: "Carsten Schultz"
    affiliations:
      - name:  "Oregon Health & Science University"
        address: 3222 SW Research Dr
        city: Portland
        state: OR
        postal-code: 97239
    orcid: 0000-0002-5824-2171
  - name: "Fikadu Tafesse"
    affiliations:
      - name:  "Oregon Health & Science University"
        address: 3222 SW Research Dr
        city: Portland
        state: OR
        postal-code: 97239
    orcid: 0000-0002-8575-4164

@@

Gaelen Guzman^1,^*, Carsten Schulz^1^, Fikadu G. Tafesse^1^

^1^ = Oregon Health & Science University; * = Corresponding author: <gaelen.guzman@lipidinteractome.org>
:::

@@

The Lipid Interactome addresses this gap by providing a structured, interactive site that adheres to FAIR data principles -- ensuring that lipid interactome studies are Findable, Accessible, Interoperable, and Reusable. Through standardized data formatting, interactive visualizations, and direct cross-study comparisons, this resource enables researchers to systematically explore the protein-binding partners of diverse bioactive lipids. By consolidating and curating lipid interactome proteomics data from multiple studies, the Lipid Interactome database serves as a critical tool for deciphering the biological functions of lipids in cellular systems.

@@

Lipid-protein interactions, proteomics, interactomics, database, multifunctionalized lipids

@@

Recent advances in developing multifunctionalized lipid analogs have revolutionized the field, enabling the systematic interrogation of lipid interactomes. These probes incorporate strategically designed functional groups that enable covalent crosslinking, affinity enrichment, and controlled activation. Most commonly, these include: (1) a diazirine ring for photoactivatable crosslinking upon exposure to 355 nm ultraviolet (UV) light, stabilizing lipid–protein interactions; (2) a terminal alkyne, permitting click chemistry-based enrichment; and, in some cases, (3) a coumarin photocage, which shields the lipid probe from premature enzymatic modification until selectively released by 405 nm light. Together, these modifications enable direct proteomic identification of lipid interactors, distinguishing true binding partners from transient or non-specific associations[@haberkantFatFabulousBifunctional2014; @schultzChemicalToolsLipid2023; @farleyTrifunctionalSphinganineNew2024a].

Several studies have already employed these lipid probes to elucidate the interactomes of key bioactive lipids, including diacylglycerol, sphingosine, sphinganine, phosphatidic acid, and phosphatidylethanolamine[@hoglingerTrifunctionalLipidProbes2017; @farleyTrifunctionalSphinganineNew2024a; @farleyTrifunctionalFattyAcid2024; @thomasTrifunctionalLipidDerivatives2025]. These studies have followed a comparative proteomics workflow, wherein crosslinked (“+UV”) and non-crosslinked (“-UV”) samples are analyzed side by side to minimize artifacts and confirm specificity[@haberkantFatFabulousBifunctional2014; @schultzChemicalToolsLipid2023]. However, despite the growing number of lipid interactome datasets, no centralized resource has existed to compile, compare, and standardize these findings.

@@

By providing a centralized platform for lipid interactome data, the Lipid Interactome significantly lowers the barriers to entry for researchers investigating lipid signaling pathways. This repository represents a necessary step toward systematizing lipid–protein interaction studies, ensuring that bioactive lipids are afforded the same level of proteomic scrutiny as their protein counterparts.

@@

At its core, the Lipid Interactome enables the direct comparison of lipid interactomes across studies, providing researchers with invaluable insights into the diverse roles that bioactive lipids play in cellular processes. By leveraging standardized data formatting and interactive visualization—including study-specific analysis pages, lipid probe aggregation, and cross-study comparisons via a Shiny application—the platform facilitates intuitive exploration of protein–lipid interactions. As a living repository, we actively encourage researchers to contribute their findings through our [Data Submission](#) page, ensuring that this resource continues to evolve alongside advancements in lipidomics research.

@@

Each study contributing to the repository is provided with a dedicated results page, allowing users to examine its findings in detail. These pages include interactive Volcano, Ranked-Order, and MA plots, which enable visualization of differential protein enrichment across experimental conditions. The plots are rendered using the Plotly and htmlwidgetsR packages, ensuring a responsive, client-side experience that supports zooming, hovering, and data filtering \[REF: Plotly, htmlwidgets\]. For transparency and reproducibility, all datasets associated with a given study are available for direct download.

@@

While there are numerous ways to quantify the mass spectrometry (MS) data, the studies included in our repository have utilized the same (or highly similar) quantitative MS pipeline using Tandem Mass Tagging\[REF\]. These datasets include those reported by Farley et al. (2024), Farley et al. (2024), and Thomas et al. (2025)[@farleyTrifunctionalSphinganineNew2024a; @farleyTrifunctionalFattyAcid2024; @thomasTrifunctionalLipidDerivatives2025]. Correspondingly, the ideal data structure for incorporation into our repository will include the following:

@@

The advent of functionalized lipid probes has fundamentally transformed lipid biology by enabling the proteomic identification of lipid-binding proteins with unprecedented specificity. However, as the number of published lipid interactome studies grows, the lack of a centralized framework for comparing and integrating these datasets presents a significant challenge. The Lipid Interactome was developed to address this need by providing researchers with a structured platform to explore, cross-reference, and build upon previous findings. By aggregating and standardizing lipid–protein interaction data, this resource facilitates the rapid identification of candidate lipid-binding proteins and supports orthogonal validation efforts.

@@

GG designed, implemented, and wrote the majority of the LipidInteractome site and manuscript. FS wrote the data analysis section of the site, provided significant intellectual contribution to the site design, and edited the manuscript. AN provided substantial editing of the site and manuscript. CS and FT provided significant intellectual contribution and text editing of the site and manuscript, and oversaw the site development.

>>>>

copyright:
  holder: "Gaelen Guzman"
  year: 2025
authors:
  - name: "Gaelen Guzman"
    affiliations:
      - name:  "Oregon Health & Science University"
        address: 3222 SW Research Dr
        city: Portland
        state: OR
        postal-code: 97239
    orcid: 0000-0002-7696-6034
    corresponding: true
    email: gaelen.guzman@lipidinteractome.org
  - name: "Frank Stein"
    affiliations:
      - name: "Proteomics Core Facility, European Molecular Biology Laboratory"
        city: Heidelberg
        country: Germany
        postal-code: 69117
    orcid: 0000-0001-9695-1692
  - name: Jeremy M. Baskin
    affiliations:
      - name: "Department of Chemistry and Chemical Biology and Weill Institute for Cell and Molecular Biology, Cornell University"
        city: Ithaca
        state: NY
        postal-code: 14853
  - name: "Carsten Schultz"
    affiliations:
      - name:  "Oregon Health & Science University"
        address: 3222 SW Research Dr
        city: Portland
        state: OR
        postal-code: 97239
    orcid: 0000-0002-5824-2171
  - name: "Fikadu Tafesse"
    affiliations:
      - name:  "Oregon Health & Science University"
        address: 3222 SW Research Dr
        city: Portland
        state: OR
        postal-code: 97239
    orcid: 0000-0002-8575-4164

@@

Gaelen Guzman^1,^*, Frank Stein^2^, Jeremy M. Baskin^3^, Carsten Schulz^1^, Fikadu G. Tafesse^1^

^1^ = Departments of Molecular Immunology and Immunology and  Chemical Physiology and Biochemistry, Oregon Health & Science University, Portland, OR, USA; ^2^ = Proteomics Core Facility, European Molecular Biology Laboratory, Heidelberg, Germany; ^3^ = Department of Chemistry and Chemical Biology and Weill Institute for Cell and Molecular Biology, Cornell University, Ithaca, NY, USA; * = Corresponding author: <gaelen.guzman@lipidinteractome.org>
:::

@@

The Lipid Interactome addresses this gap by providing a structured, interactive web portal that adheres to FAIR data principles -- ensuring that lipid interactome studies are Findable, Accessible, Interoperable, and Reusable. Through standardized data formatting, interactive visualizations, and direct cross-study comparisons, this resource enables researchers to systematically explore the protein-binding partners of diverse bioactive lipids. By consolidating and curating lipid interactome proteomics data from multiple studies, the Lipid Interactome database serves as a critical tool for deciphering the biological functions of lipids in cellular systems.

@@

Lipid-protein interactions, proteomics, interactomics, database, multifunctionalized lipids, photoaffinity labeling

@@

Recent advances in developing multifunctionalized lipid analogs have revolutionized the field, enabling the systematic interrogation of lipid interactomes. These probes incorporate strategically designed functional groups that enable covalent crosslinking, affinity enrichment, and controlled activation. Most commonly, these include: (1) a diazirine group for photoactivatable crosslinking upon exposure to 355 nm ultraviolet (UV) light, stabilizing non-covalent and often modest-affinity lipid–protein interactions; (2) a terminal alkyne, permitting click chemistry-based enrichment; and, in some cases, (3) a coumarin photocage, which shields the lipid probe from premature enzymatic modification until it is selectively cleaved by 405 nm light (a wavelength that does not induce diazirine photolysis). Together, these modifications enable direct proteomic identification of lipid interactors, distinguishing true binding partners from transient or non-specific associations[@haberkantFatFabulousBifunctional2014; @schultzChemicalToolsLipid2023; @farleyTrifunctionalSphinganineNew2024a].

Several studies have already employed these lipid probes to elucidate the interactomes of key bioactive lipids, including diacylglycerol, sphingosine, sphinganine, phosphatidic acid, and phosphatidylethanolamine, N-acylphosphatidylethanolamine, and  phosphatidyl alcohol[@hoglingerTrifunctionalLipidProbes2017; @farleyTrifunctionalSphinganineNew2024a; @farleyTrifunctionalFattyAcid2024; @thomasTrifunctionalLipidDerivatives2025; @chiuPhotoaffinityLabelingReveals2025; @yuChemoproteomicsApproachProfile2022]. These studies have followed a comparative proteomics workflow, wherein crosslinked (“+UV”) and non-crosslinked (“-UV”) samples are analyzed side by side to minimize artifacts and confirm specificity[@haberkantFatFabulousBifunctional2014; @schultzChemicalToolsLipid2023]. However, despite the growing number of lipid interactome datasets, no centralized resource has existed to compile, compare, and standardize these findings.

@@

By providing a centralized platform for lipid interactome data, the Lipid Interactome significantly lowers the barriers to entry for researchers investigating lipid signaling pathways, enabling hypothesis generation through comparative analysis of multiple studies. Overall, this repository represents an important step toward systematizing lipid–protein interaction studies, ensuring that bioactive lipids are afforded the same level of proteomic scrutiny as their protein counterparts.

@@

At its core, the Lipid Interactome enables the direct comparison of lipid interactomes across studies, providing researchers with invaluable insights into the diverse roles that bioactive lipids play in cellular processes. By leveraging standardized data formatting and interactive visualization—including study-specific analysis pages, lipid probe aggregation, and cross-study comparisons via a Shiny application—the platform facilitates intuitive exploration of protein–lipid interactions. As a living repository, we actively encourage researchers to contribute their findings through our [Data Submission](https://www.lipidinteractome.org/contactus/datasubmission) page, ensuring that this resource continues to evolve alongside advancements in lipidomics research.

@@

Each study contributing to the repository is provided with a dedicated results page, allowing users to examine its findings in detail. These pages include interactive Volcano, Ranked-Order, and MA plots, which enable visualization of differential protein enrichment across experimental conditions. The plots are rendered using the Plotly and htmlwidgetsR packages, ensuring a responsive, client-side experience that supports zooming, hovering, and data filtering[@plotly; @ramnathvaidyanathanHtmlwidgetsHTMLWidgets2015]. For transparency and reproducibility, all datasets associated with a given study are available for direct download.

@@

While there are numerous ways to quantify the mass spectrometry (MS) data, the majority of studies included in our repository have utilized the same (or highly similar) quantitative MS pipeline using Tandem Mass Tagging[@thompsonTandemMassTags2003]. These datasets include those reported by Farley et al. (2024), Farley et al. (2024), and Thomas et al. (2025)[@farleyTrifunctionalSphinganineNew2024a; @farleyTrifunctionalFattyAcid2024; @thomasTrifunctionalLipidDerivatives2025]. Some studies have also featured quantitative MS analysis using stable isotope labeling of amino acids in cell culture (SILAC), which also enables extraction of key data described below[@chiuPhotoaffinityLabelingReveals2025; @yuChemoproteomicsApproachProfile2022]. Correspondingly, the ideal data structure for incorporation into our repository will include the following:

@@

The advent of functionalized lipid probes has fundamentally transformed lipid biology by enabling the proteomic identification of lipid-binding proteins with unprecedented specificity. However, as the number of published lipid interactome studies grows, the lack of a centralized framework for comparing and integrating these datasets presents a significant challenge for deciphering biological functions of individual lipids and lipid-binding proteins holistically and identifying trends across datasets. The Lipid Interactome was developed to address this need by providing researchers with a structured platform to explore, cross-reference, and build upon previous findings. By aggregating and standardizing lipid–protein interaction data, this resource facilitates the rapid identification of candidate lipid-binding proteins and supports orthogonal validation efforts.

@@

GG designed, implemented, and wrote the majority of the LipidInteractome repository and manuscript. FS wrote the data analysis section of the repository, provided significant intellectual contribution to the repository design, and edited the manuscript. AN provided substantial editing of the repository and manuscript. JMB edited the manuscript and contributed data to the repository. CS and FT provided significant intellectual contribution and text editing of the repository and manuscript, and oversaw the site development.

### 2025-03-31 IndividualStudies/WY_2021.qmd
Adding Yu et al 2021 to yaml, adding JMB edits to manuscript

>>>>

#### Gene Ontology Analysis

**In beta: GO analysis still under development**

:::::{.border}
::::{#fig-PE_GOplots}
::: {.panel-tabset}

##### Cell Compartment

<iframe src="/LipidProbe/GO_plots/PDAA_WY_2021_CC-DOTplot.html" width="100%" height="500px"></iframe>

##### Molecular Function

No enriched molecular functions identified among enriched hits and candidates.

##### Biological Process

No enriched biological processes identified among enriched hits and candidates.

GO Dot plots display the enrichment of GO terms among the proteins enriched to the probe. For these analyses, only proteins categorized as "enriched candidates" and "enriched hits" were subject to GO analysis. The Cell Compartment analysis assesses whether the list of enriched proteins contains a statistically significant number of proteins in the same cellular region; appropriately, the Molecular Function and Biological Process analyses does the same for molecular function and biological process, respectively. [Click here for more information about Gene Ontology Analysis.](/Background/DataAnalysisAndStatistics.qmd#gene-ontology-overview) 
::::
:::::

### 2025-03-31 LipidProbe/Phosphatidylalcohol.qmd
Adding Yu et al 2021 to yaml, adding JMB edits to manuscript

---
title: "Yu et al. 2021"
subtitle: "A Chemoproteomics Approach to Profile Phospholipase D-Derived Phosphatidyl Alcohol Interactions"
date: 2021-12-15
format: 
  html:
    embed-resources: false
standalone: false
---

@@

```{r HiddenDataWrangling, include=FALSE, echo=FALSE}

# RawData <- read_csv(here::here("IndividualStudies/DataTables/WY_2021_ACSChemBio_RawData.csv")) |>
#   filter(Coverage != 0 & Fold_change != 0) |>
#   mutate(gene_name = gene_name...3) |>
#   group_by(gene_name) |>
#   summarise(logFC = mean(log2(Fold_change)),
#             # pvalue = mean(pvalue),
#             numReplicates = n(),
#             AveExpr = log10(mean(Control_abundance) + mean(Sample_abundance)/2)) |>
#   arrange(-logFC)

# median_logFC <- median(RawData$logFC)

# RawData$logFC <- RawData$logFC - median_logFC

# RawData <- RawData |> 
#   mutate(LipidProbe = "PDAA",
#         AveExpr = case_when(.default = AveExpr,
#                               AveExpr == -Inf ~ 0),
#                               hit_annotation = case_when(.default = "no hit",
#                                                           logFC >= 0.5849625 & numReplicates == 2 ~ "enriched candidate",
#                                                           logFC >= 0.5849625 & numReplicates == 3 ~ "enriched hit")) |>         
#   glimpse()

# write_csv(RawData, here("IndividualStudies/DataTables/WY_2021_ACSChemBio_Download.csv"))

```{r Setup_Data_Wrangling, include=FALSE, echo=FALSE}
## intitialize libraries
library(here)
library(biomaRt)
library(rentrez)

@@

## Data visualization

@@

```{r, echo=FALSE, warning=FALSE}
#| fig-cap: "Data as reported in [Yu et al., 2021, 2024](/IndividualStudies/WY_2021.qmd). Black proteins are identified in only one replicate, Purple enriched candidates are defined as proteins identified in two replicates & fold-change > 1.5 (logFC 0.585) & pvalue < 0.01, and Orange enriched hits are defined as proteins identified in all three replicates & fold-change > 1.5 (logFC 0.585) & pvalue < 0.01)."

@@

##### MA plot

```{r, echo=FALSE, warning=FALSE}
#| fig-cap: "Data as reported in [Yu et al., 2021](/IndividualStudies/WY_2021.qmd). Black proteins are identified in only one replicate, Purple enriched candidates are defined as proteins identified in two replicates & fold-change > 1.5 (logFC 0.585) & pvalue < 0.01, and Orange enriched hits are defined as proteins identified in all three replicates & fold-change > 1.5 (logFC 0.585) & pvalue < 0.01)."

MASpecial(data)
```

@@

## Data exploration

@@

@@

## Data download

{{< downloadthis DataTables/WY_2021_ACSChemBio_Download.csv dname="WY_2021_ACS-ChemBio_Download">}}

>>>>

---
title: "Phosphatidyl diazirine alkyne alcohol"
subtitle: "PDAA"
format: 
  html:
    embed-resources: false
callout-icon: false
---

## Structure

:::{.border}
::: {layout="[[100], [-25, 50, -25], [100]]"}
![(A) Native Phosphatidylethanol.](/LipidProbe/Structures/POH.png)

![(B) Diazirine alkyne alcohol.](/LipidProbe/Structures/DAA.png)

![(C) Phosphatidyl diazirine alkyne alcohol (PDAA).](/LipidProbe/Structures/PDAA.png)

Temporary chemical structures drawn by Gaelen Guzman.
:::
:::

## Protein Interactome

@@

```{r PDAA_setup, include=FALSE, echo=FALSE}
## intitialize libraries
library(here)
library(biomaRt)
library(rentrez)

@@

#### Data visualization

@@

```{r, echo=FALSE, warning=FALSE}
#| fig-cap: "Data as reported in [Farley et al., 2024](/IndividualStudies/SF_2024.qmd). Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV)."

@@

##### MA Plot

```{r, echo=FALSE, warning=FALSE}
#| fig-cap: "Data as reported in [Farley et al., 2024](/IndividualStudies/SF_2024.qmd). Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV)."

MASpecial(data)

@@

#### Data exploration and download

Check the boxes below to filter by significance thresholds.

@@

```
:::

@@

{{< downloadthis DataSets/PDAA_WY_2021_ACSChemBio_Download.csv dname="PDAA_WY_2021_ACSChemBio_download">}}

### 2025-03-31 LipidProbe/Sphinganine.qmd
putting NAPE on the index
example
adding WY_2021 study, checking if authors like it
Adding Yu et al 2021 to yaml, adding JMB edits to manuscript

---
title: "Trifunctional Sphinganine"
prefer-html: true
format: html
callout-icon: false
---

@@

::: {.panel-tabset}

@@

:::{.border}
```{r, echo=FALSE, warning=FALSE}
#| fig-cap: "Data as reported in [Farley et al., 2024](/IndividualStudies/SF_2024.qmd). Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV)."

VolcanoPlotStandardized(data)
```
:::

@@

:::{.border}
```{r, echo=FALSE, warning=FALSE}
#| fig-cap: "Data as reported in [Farley et al., 2024](/IndividualStudies/SF_2024.qmd). Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV)."

RankedOrderPlotStandard(data)
```
:::

@@

:::{.border}
```{r, echo=FALSE, warning=FALSE}
#| fig-cap: "Data as reported in [Farley et al., 2024](/IndividualStudies/SF_2024.qmd). Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV)."

@@

```
:::
:::

## Gene Ontology Analysis

>>>>

---
title: "Trifunctional Sphinganine"
format: 
  html:
    embed-resources: false
callout-icon: false
---

@@

#### Data visualization

::::{.border}
::: {.panel-tabset}

@@

```{r, echo=FALSE, warning=FALSE}
#| fig-cap: "Data as reported in [Farley et al., 2024](/IndividualStudies/SF_2024.qmd). Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV)."

VolcanoPlotStandardized(data)
```

@@

```{r, echo=FALSE, warning=FALSE}
#| fig-cap: "Data as reported in [Farley et al., 2024](/IndividualStudies/SF_2024.qmd). Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV)."

RankedOrderPlotStandard(data)
```

@@

```{r, echo=FALSE, warning=FALSE}
#| fig-cap: "Data as reported in [Farley et al., 2024](/IndividualStudies/SF_2024.qmd). Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV)."

@@

```
:::
::::

#### Gene Ontology Analysis

### 2025-03-31 StudyInformation_includes/DCC_2025_include.qmd
Adding Yu et al 2021 to yaml, adding JMB edits to manuscript

<a href="/LipidProbe/N-Acylphosphatidylethanolamine.qmd" class="hover-preview">Bifunctional NAPE</a>
<span class="hover-image">
  <img src="/LipidProbe/Structures/BF_NAPE.png" alt="Bifunctional NAPE" />
</span>

>>>>

<a href="/LipidProbe/N-Acylphosphatidylethanolamine.qmd" class="hover-preview">Bifunctional NAPE</a>
<span class="hover-image">
  <img src="/Structures/BF-NAPE.png" alt="Bifunctional NAPE" />
</span>

### 2025-03-31 StudyInformation_includes/WY_2021_include.qmd
Adding Yu et al 2021 to yaml, adding JMB edits to manuscript

PDAA

<!-- 
<a href="/LipidProbe/N-Acylphosphatidylethanolamine.qmd" class="hover-preview">Bifunctional NAPE</a>
<span class="hover-image">
  <img src="/LipidProbe/Structures/BF_NAPE.png" alt="Bifunctional NAPE" />
</span> -->

>>>>

<a href="/LipidProbe/PhosphatidylAlcohol.qmd" class="hover-preview">Phosphatidyl Alcohol</a>
<span class="hover-image">
  <img src="/LipidProbe/Structures/PDAA.png" alt="Phosphatidyl diazirine alkyne alcohol" />
</span>

### 2025-03-31 index.qmd
example
Adding Yu et al 2021 to yaml, adding JMB edits to manuscript

---
title: "The Lipid Interactome Repository"
format: 
  html:
    embed-resources: true
standalone: true
---

@@

>>>>

---
title: "The Lipid Interactome Repository"
format: 
  html:
    embed-resources: false
standalone: false
---

@@

  <a href="LipidProbe/PhosphatidylAlcohol.qmd" style="text-decoration: none;">
      <button style="background-color:rgb(41, 204, 131); color: white; font-size: 20px; padding: 15px 30px; border: none; border-radius: 8px; margin: 10px; cursor: pointer;">
          Phosphatidyl Alcohol
      </button>
  </a>
